clusters

### 2015-07-20 cluster.rmd
first inn

# library('RcmdrPlugin.BCA')
library(devtools)
library('ggbiplot')
library('fpc')
library('vegan')
library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('dendextend')
library('FNN')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

all7d<- all7c %>% select(inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos)

@@

>>>>

library('RcmdrPlugin.BCA')
library(devtools)
library('ggbiplot')
library('fpc')
library('vegan')
library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('dendextend')
library('FNN')
library('caret')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

all7d<- all7c %>% select(mlsto, inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos, return.pdol, cost.mlsto, hrs.mlsto)

@@

Retrieve nearest neighbour - numeric first

```{r knn, echo=FALSE}
#pretend you are predicting .. post code

inv.knn<- function(df= all7d, predict= 'inv.mlsto', new.cases= c(1000), k=3){
        inv.knn = knn(df[,predict], df[new.cases,predict],
                df$pc.pro, k=k)
        indices<- attr(inv.knn,  "nn.index")
        #checkout the nearest neigbours!
        df %>% slice(c(new.cases,indices[1,])) %>% print

        }
inv.knn(df= all7d, predict= 'inv.mlsto', new.cases= 2000, k=3)
